Tracking Rodinia into the Neoproterozoic: new paleomagnetic constraints from the Jacobsville Formation

### 2024-01-27 Manuscript/Manuscript.tex
sync notebooks, some figures, data files, and manuscript after proof correction

\section*{Data Availability}
Paleomagnetic data associated with this study are available within the MagIC database (\url{10.7288/V4/MAGIC/19780}) and all data are within a Github repository associated with this work (\url{https://github.com/Swanson-Hysell-Group/Jacobsville}) that is also archived on Zenodo (\url{https://doi.org/XXX}; \textit{will be archived in Zenodo upon acceptance}). This repository also contains Python code that implements all of the calculations, visualizations and statistical tests discussed herein.

>>>>

\section*{Data Availability}
Paleomagnetic data associated with this study are available within the MagIC database (\url{10.7288/V4/MAGIC/19780}) and all data are within a Github repository associated with this work (\url{https://github.com/Swanson-Hysell-Group/Jacobsville}) that is also archived on Zenodo (\url{https://zenodo.org/doi/10.5281/zenodo.10556464}; \textit{will be archived in Zenodo upon acceptance}). This repository also contains Python code that implements all of the calculations, visualizations and statistical tests discussed herein.
